\LARGE \bf Steering a Swarm Using Global Inputs and Swarm Statistics

### 2016-08-12 journalSwarmControl/Introduction.tex
added Mable's edits

Our experiments show that numerous simple robots responding to global control inputs are directly controllable by a human operator without special training, that the visual feedback of the swarm state should be simple to increase task performance, and that humans perform swarm-object manipulation faster using attractive control schemes than repulsive control schemes.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{CompleteMazeDescription.pdf}\end{overpic}
\begin{overpic}[width=0.438\columnwidth]{MainExpFig.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the first and second moments of the robot distribution.  Here a swarm of simple robots (blue discs) pushes a green hexagon toward the goal. Simulation at left, screen capture form hardware experiment at right. See multimedia extension.}
\end{figure}
 %function and implementation function

>>>>

Our online experiments show that numerous simple robots responding to global control inputs are directly controllable by a human operator without special training, that the visual feedback of the swarm state should be simple to increase task performance, and that humans perform swarm-object manipulation faster using attractive control schemes than repulsive control schemes.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{CompleteMazeDescription.pdf}\end{overpic}
\begin{overpic}[width=0.438\columnwidth]{MainExpFig.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the mean and variance of the robot distribution.  Here a swarm of simple robots (blue discs) pushes a green hexagon toward the goal. Simulation at left, screen capture from hardware experiment at right. See multimedia extension.}
\end{figure}
 %function and implementation function

### 2016-08-12 journalSwarmControl/experiment.tex
added Mable's edits

This section analyzes an \emph{object manipulation} task attempted by both our hybrid, hysteresis-based controller, inspired by the analysis of human users in \S \ref{sec:expResults}.  
The swarm must deliver the object to the goal region.  To solve this object manipulation task, we divide the task into two components: designing a policy for the object, and designing a control law for the swarm to push the object according to the policy.

@@

The variance controller in Alg.~\ref{alg:MeanVarianceControl} is a greedy algorithm that is susceptible to outliers. The controller in \cite{Shahrokhi2015} failed in $14\%$ trials, often because workspace obstacles made some robots unable to reach the object. This failure rate increases if  object weight increases or ground-robot friction increases. The mean and covariance calculations \eqref{eq:meanVar} included all robots in the workspace. Robots that cannot reach the object due to obstacles skew these calculations. The state machine in Fig.\ \ref{fig:Region} solves this problem by creating two states for the maze: either main or transfer. Each state has a set of regions representing a discretized visibility polygon. Whenever the object crosses a region boundary the state toggles. The main regions are generated by extending obstacles until they meet another obstacle. The transfer regions are perpendicular to obstacle boundaries, and act as a buffer between two main regions.
This filtering increases experimental success because the mean calculation only includes nearby robots that can directly interact with the object. 
%In the example, we want the robots to push the object to the right. Without filtering the robots, the orange star is the mean and the algorithm would instruct the robots to push the object southeast. The filtered mean is at the yellow star and the algorithm instructs the robots to push the object directly east. 
%When the object leaves main region 1 the maze state switches to transfer. 
%The object is in transfer region 0, so only robots in transfer region 0 are included in the mean and covariance calculations.  
%This heuristic improves performance by $50\%$ or less regarding the object heaviness.
In 10 simulations with 100 robots, completion time without outlier rejection required $\mu=245, \sigma=135$ s while using outlier rejection required $\mu=90, \sigma=35$ s.
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

\begin{figure*}
\begin{center}
	\begin{overpic}[width=0.6\columnwidth]{stateMachine.pdf}\end{overpic}\\
	\begin{overpic}[width=0.45\columnwidth]{mainRegions.pdf}\end{overpic}
	\begin{overpic}[width=0.45\columnwidth]{transferRegions.pdf}\end{overpic}
\end{center}
\vspace{-0.5em}
\caption{\label{fig:Region}  Outlier rejection state machine and regions.
}
\end{figure*}

\subsection{Algorithm for object manipulation}
 We use the hybrid hysteresis-based controller in Alg.~\ref{alg:MeanVarianceControl}  to track the desired position, while maintaining sufficient robot density to move the object by switching to minimize variance whenever variance exceeds a set limit. The minimize variance control law \eqref{eq:PDcontrolVariance} is slightly modified to choose the nearest corner further from the goal than $\mathbf{b}$ with an obstacle-free straight-line path to $\mathbf{b}$. 
The control algorithm  for object manipulation is listed in Alg.~\ref{alg:BlockPushing}.

In rare cases during simulations the swarm may become trapped in a local minima of \eqref{eq:potentialfield}.
If the swarm mean position does not change for ten seconds, the swarm is assumed to be in a local minima and is commanded to move toward the previous corner. As soon as the mean position changes, normal control resumes.

@@

\subsection{Automated object manipulation (simulation)}
Fig.~\ref{fig:story} shows snapshots during an execution of this algorithm in simulation. 
Experimental results of parameters sweeps are summarized in Fig.~\ref{fig:AutoVeryParam}.  Each trial measured the time to deliver the object to the goal location.  The default parameter settings used 100 robots, a normalized weight of 1, a hexagon shape, and Brownian noise (applied each simulation step) with $W=5$.

>>>>

This section analyzes an \emph{object manipulation} task attempted by our hybrid, hysteresis-based controllers, inspired by the analysis of human users in \S \ref{sec:expResults}.  
The swarm must deliver the object to the goal region.  To solve this object manipulation task, we divide the task into two components: designing a policy for the object, and designing a control law for the swarm to push the object according to the policy.

@@

The variance controller in Alg.~\ref{alg:MeanVarianceControl} is a greedy algorithm that is susceptible to outliers. The controller in \cite{Shahrokhi2015} failed in $14\%$ trials, often because workspace obstacles made some robots unable to reach the object. This failure rate increases if  object weight increases or ground-robot friction increases. The mean and covariance calculations \eqref{eq:meanVar} included all robots in the workspace. Robots that cannot reach the object due to obstacles skew these calculations. The state machine in Fig.\ \ref{fig:Region}A solves this problem by creating two states for the maze: either main or transfer. Each state has a set of regions representing a discretized visibility polygon. Whenever the object crosses a region boundary the state toggles. The main regions are generated by extending obstacles until they meet another obstacle. The transfer regions are perpendicular to obstacle boundaries, and act as a buffer between two main regions.

Fig.\ \ref{fig:Region}B shows the regions for the main state. The object is in region 1. An indicator function is applied to \eqref{eq:meanVar} so only robots inside region 1 are counted.  This filtering increases experimental success because the mean calculation only includes nearby robots that can directly interact with the object. 
When the object leaves main region 1 the state switches to transfer. The transfer regions are shown in Fig. 3.  The object is in transfer region 1, so only robots in transfer region 1 are included in the mean and covariance calculations. 
In Fig.\ \ref{fig:Region}C, the robots should push the object to the left. Without filtering using regions, the red circle is the mean and the algorithm would instruct the robots to push the object up. The black circle shows the filtered mean and the algorithm instructs the robots to push the object directly left.

In 10 simulations with 100 robots, completion time without outlier rejection required $\mu=245, \sigma=135$ s while using outlier rejection required $\mu=90, \sigma=35$ s.
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

\begin{figure*}
\begin{center}
	\begin{overpic}[width=0.6\columnwidth]{stateMachine.pdf}\put(-12,25){A}\end{overpic}\\
	~~\begin{overpic}[width=0.45\columnwidth]{mainRegions.pdf} %,grid=true
	\put(-6,85){B}
	\end{overpic}
	~~
	\begin{overpic}[width=0.45\columnwidth]{transferRegions.pdf}
	\put(-6,85){C}
	\end{overpic}
\end{center}
\vspace{-0.5em}
\caption{\label{fig:Region}  Outlier rejection state machine and regions.
}
\end{figure*}

\subsection{Algorithm for object manipulation}
 We use the hybrid hysteresis-based controller in Alg.~\ref{alg:MeanVarianceControl}  to track the desired position, while maintaining sufficient robot density to move the object by switching to minimize variance whenever variance exceeds a set limit.  The min and max variance limits from  \label{eq:sigMaxMin} incremented by $0.003 W$ and $0.006 W$.
 The minimize variance control law \eqref{eq:PDcontrolVariance} is slightly modified to choose the nearest corner further from the goal than $\mathbf{b}$ with an obstacle-free straight-line path to $\mathbf{b}$. 
The control algorithm  for object manipulation is listed in Alg.~\ref{alg:BlockPushing}.

In rare cases during simulations the swarm may become trapped in a local minima of \eqref{eq:potentialfield}.
If the swarm mean position does not change for five seconds, the swarm is assumed to be in a local minima and is commanded to move toward the previous corner. As soon as the mean position changes, normal control resumes.

@@

\subsection{Automated object manipulation (simulation)}
Fig.~\ref{fig:story} shows snapshots during an execution of this algorithm in simulation. 
Experimental results of parameters sweeps are summarized in Fig.~\ref{fig:AutoVeryParam}.  Each trial measured the time to deliver the object to the goal location.  The default parameter settings used 100 robots, a normalized weight of 1, a hexagon shape, and Brownian noise (applied once each simulation step) with $W=5$.
